---
title: "Project proposal"
author: "Chrissy & Ricky"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(readr)
library(broom)
library(fivethirtyeight)
library(WDI)
```

## 0. Requirements
You will write your proposal in the proposal.Rmd file in your Github project.

Section 1 - Introduction: The introduction should introduce your general research question and your data (where it came from, how it was collected, what are the cases, what are the variables, etc.).

Section 2 - Data: Place your data in the /data folder, and add dimensions and codebook to the README in that folder. Then print out the output of glimpse() or skim() of your data frame.

Section 3 - Data analysis plan:

1. The outcome (response, Y) and predictor (explanatory, X) variables you will use to answer your question. The comparison groups you will use, if applicable.

2. Very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. (You can add to these later as you work on your project.)

3. The statistical method(s) that you believe will be useful in answering your question(s). (You can update these later as you work on your project.)
What results from these specific statistical methods are needed to support your hypothesized answer?

Finally, each section should be no more than 1 page (excluding figures). You can check a print preview to confirm length.

## 1. Introduction

Section 1 - Introduction: The introduction should introduce your general research question and your data (where it came from, how it was collected, what are the cases, what are the variables, etc.).

1. We intend on using covid and world indicator to examine what cause differences in how different countries experienced the pandemic/ what caused different pandemic outcomes across the world. 

We will use data from two sources: (1) Covid-19 related data (owid-covid data), (2) World Bank World Development Indicator. Covid-related data is coming from this repo: https://github.com/owid/covid-19-data.git; WDI is coming from the WDI package in R. The owid-covid-data should be sufficient for our analysis, but we may need additional data from WDI, so we include WDI here in case we may need it in the future.


## 2. Data

Section 2 - Data: Place your data in the /data folder, and add dimensions and codebook to the README in that folder. Then print out the output of glimpse() or skim() of your data frame.


```{r import_data}
covid_data <- readr::read_csv(file = "../data/owid-covid-data.csv")
covid_data_code <- readr::read_csv(file = "../data/owid-covid-codebook.csv")
```

```{r view_data}
glimpse(covid_data)
view(covid_data_code)
```

As mentioned eariler, we may not use the following data, but I just include them in case we may use if as we move on for our project:
```{r WDI}
example <- WDI(indicator = c("SP.RUR.TOTL.ZS", "EN.ATM.CO2E.PC", "SP.POP.GROW", extra = TRUE))
glimpse(example)
view(example)
```

```{r fivethirtyeight}
view(US_births_2000_2014)
view(US_births_1994_2003)
```

## 3. Data analysis plan

Section 3 - Data analysis plan:

1. The outcome (response, Y) and predictor (explanatory, X) variables you will use to answer your question. The comparison groups you will use, if applicable.

- our outcome/ y variables would be deaths and other covid related markers like ICU occupation and overall cases. 
- the explanatory variables would be taken from the world bank data and covid data and could include medical resources like ICU beds or number of doctors. We could also subset the data and examine the effect of vaccination rate on these covid indicators. 


2. Very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. (You can add to these later as you work on your project.)

sapply(covid_data, mean, na.rm=TRUE)
summary(covid_data)
-
-

3. The statistical method(s) that you believe will be useful in answering your question(s). (You can update these later as you work on your project.)
What results from these specific statistical methods are needed to support your hypothesized answer?

- 
-
-




