---
title: "Covid-19, Global Pandemic, and Data Science"
subtitle:
author: "Team Chrissy & Ricky <br> Chrissy Aman and Ricky Sun"
institute: "Bates College"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

#xaringan::inf_mr()
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r title-page-pic, include=FALSE}
style_xaringan(
  title_slide_background_image = "img/covid.jpg"
)
```

## Outline 

- Introduction

- Literature Review

- Our Data  

- Methods & Data Analyses

- Results

- Limitations and Potential Future Studies

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

---

## Research Question

- In our research, we are trying to use Covid-19 related data, together with other relevant
data to find potential predictors for Covid-19 cases, deaths, or vaccination rates. 

? how to add a navigation bar below 

? how to change font size

? how to adjust positioning of texts

---

class: inverse, center, middle

# Introduction
? How to add background pic 

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)
---

# Introduction 

COVID-19, also known as Coronavirus disease 2019 is a contagious disease caused by a virus, the severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2)

Up until yesterday, there are over xxx infections and xxx deaths since the beginning of 2020

Although no one can predict a pandemic like this, with the help of data, we might be able to use available data to, for example, evaluate risks, so that the virus can be better managed or even contained in earlier stages. 

---

class: inverse, middle, center

# Literature Review

```{r section-title-pic, include=FALSE}
style_xaringan(
  title_slide_background_image = "img/covid.jpg"
)
```

---

# Literature Review - [1]


---

# Literature Review - [2 Covid-19 and meta-analyses of research]

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7607482/

---
# Literature Review - [3: Covid-19 and weather]

https://www.nature.com/articles/s41598-021-01189-3

Rising temperature levels during spring and summer are often argued to enable lifting of strict containment measures even in the absence of herd immunity. Despite broad scholarly interest in the relationship between weather and coronavirus spread, previous studies come to very mixed results. To contribute to this puzzle, the paper examines the impact of weather on the COVID-19 pandemic using a unique granular dataset of over 1.2 million daily observations covering over 3700 counties in nine countries for all seasons of 2020. Our results show that temperature and wind speed have a robust negative effect on virus spread after controlling for a range of potential confounding factors. These effects, however, are substantially larger during mealtimes, as well as in periods of high mobility and low containment, suggesting an important role for social behaviour.

---

# Literature Review - [4: COVID-19 vaccines and economic activity]

https://sjes.springeropen.com/articles/10.1186/s41937-021-00082-0

https://www.sciencedirect.com/science/article/pii/S0929664621002357


This paper empirically examines the economic effects of COVID-19 vaccine rollouts using a cross-country daily database of vaccinations and high-frequency indicators of economic activity—nitrogen dioxide (NO2) emissions, carbon monoxide (CO) emissions, and Google mobility indices—for a sample of 46 countries over the period December 16, 2020 to June 20, 2021. Using surprises in vaccines administered, we find that an unexpected increase in vaccination per capita is associated with a significant increase in economic activity. We also find evidence for nonlinear effects of vaccines, with the marginal economic benefits being larger when vaccination rates are higher. Country-specific conditions play an important role, with lower economic gains if strict containment measures are in place or if the country is experiencing a severe outbreak. Finally, the results provide evidence of spillovers across borders, highlighting the importance of equitable access to vaccines across nations.

---

# Literature Review - [5: Covid-19 and social media]

The COVID-19 risk perception: A survey on socioeconomics and media attention

This brief communication examines the role of socioeconomic factors and use of social media on the risk perception about COVID-19 in Vietnam, which shares a common border with China. Moreover, Vietnam was the first country to succeed in containment of severe acute respiratory syndrome (SARS) in 2003. From a sample of 391 Vietnamese respondents aged from 15 to 47 years, the present study found that geographical regions and behaviors in using social media have a positive impact on the risk perception of COVID-19 epidemic in Vietnam. It also adds to the significance of understanding the risk perception among people to communicate the public health response to COVID-19 to curb the spread of this deadly virus.

---

# Literature Review - [6]

---

class: inverse, middle, center

# Our Data

---

## Our Data - details

We used the COVID-19 dataset from "Our World in Data", where they combined multiple datasets together from CDC, John Hopkins, WDI,....

---

class: inverse, middle, center

# Methods & Data Analyses

---

# Methods & Data Analyses - details

We have three major parts of analyses:
1. preliminary exploration like summary statistics, scatter plots, correlations, maps

2. Regression analyses, ranging from OLS, Diff in Diff, regression continuity

3. Advanced models and machine learning algorithnms

---

# Methods & Data Analyses - details

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

---

class: inverse, middle, center

# Results & Implications [1: preliminary analyses]

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

how to adjust transparency of background pic

---

# Results & Implications - [2a: regression analyses - simple linear regression]

```{r linear-model-1}
linear_reg() %>%
  set_engine("lm") %>%
  fit(total_cases_per_million ~ population_density + hospital_beds_per_thousand, data = covid_country) %>%
  tidy()
```

```{r linear-model-2}
linear_reg() %>%
  set_engine("lm") %>%
  fit(total_cases_per_million ~ population_density + hospital_beds_per_thousand, data = covid_country) %>%
  tidy()
```

---

# Results & Implications - [2b: regression analyses - other]


---

# Results & Implications - [3: machine learnng]


---

class: inverse, middle, center

# Limitations and Potential Future Studies

---

# Limitations - details


---

# Future Studies

---

# References

[1] Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

[2] You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

[3]

[4]

---
