---
title: "Covid-19, Global Pandemic, and Data Science"
subtitle:
author: "Team Chrissy & Ricky <br> Chrissy Aman and Ricky Sun"
institute: "Bates College"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

#xaringan::inf_mr()
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r title-page-pic, include=FALSE}
style_xaringan(
  title_slide_background_image = "img/covid.jpg"
)
```

## Outline 

- Introduction

- Literature Review

- Our Data  

- Methods & Data Analyses

- Results

- Limitations and Potential Future Studies

---

## Research Question

- In our research, we are trying to use Covid-19 related data, together with other relevant
data to find potential predictors for Covid-19 cases, deaths, or vaccination rates. 

? how to add a navigation bar below 

? how to change font size

? how to adjust positioning of texts

---

class: inverse, center, middle

# Introduction

```{r section-title-pic, include=FALSE}
style_xaringan(
  title_slide_background_image = "img/covid.jpg"
)
```

---

# Introduction 

COVID-19, also known as Coronavirus disease 2019 is a contagious disease caused by a virus, the severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2)

Up until yesterday, there are over xxx infections and xxx deaths since the beginning of 2020

Although no one can predict a pandemic like this, with the help of data, we might be able to use available data to, for example, evaluate risks, so that the virus can be better managed or even contained in earlier stages. 

---

class: inverse, middle, center

# Literature Review

```{r section-title-pic, include=FALSE}
style_xaringan(
  title_slide_background_image = "img/covid.jpg"
)
```

---

# Literature Review - [1]


---

# Literature Review - [2]


---
# Literature Review - [3: Covid-19 and weather]

Rising temperature levels during spring and summer are often argued to enable lifting of strict containment measures even in the absence of herd immunity. Despite broad scholarly interest in the relationship between weather and coronavirus spread, previous studies come to very mixed results. To contribute to this puzzle, the paper examines the impact of weather on the COVID-19 pandemic using a unique granular dataset of over 1.2 million daily observations covering over 3700 counties in nine countries for all seasons of 2020. Our results show that temperature and wind speed have a robust negative effect on virus spread after controlling for a range of potential confounding factors. These effects, however, are substantially larger during mealtimes, as well as in periods of high mobility and low containment, suggesting an important role for social behaviour.

---

# Literature Review - [4]


---

# Literature Review - [5]

---

# Literature Review - [6]

---

class: inverse, middle, center

# Our Data

---

## Our Data - details

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

class: inverse, middle, center

# Methods & Data Analyses

---

# Methods & Data Analyses - details

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Methods & Data Analyses - details

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

class: inverse, middle, center

# Results & Implications

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Results & Implications - details

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

class: inverse, middle, center

# Limitations and Potential Future Studies

---

# Limitations and Potential Future Studies - details

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.

---

# References

[1] Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

[2] You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

---
